Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-04-17 paper/paper.tex
start procedure

\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 1. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.

@@

\subsection[short]{Procedure}
Procedure

>>>>

\subsection[short]{Equipment}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup although both were running on Sonoma or MacOS 14. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.

@@

\subsection[short]{Procedure}
After signing consent forms, each participant was explained the overall concept of what they would be doing. First they would take the short typing test three times to account for the three levels of music.
